Bird beak's elaboration and exploration

### 2022-03-25 Analysis/02-mcmcmcglmmm_analysis.Rmd
Added passerines bits

>>>>

## Passeriformes focus

## Loading the parametrisation data
load(file = "../Data/Processed/shapsepace_passeriformes_suborder_family.rda")

## Select the data
shapespace <- shapsepace_passeriformes_suborder_family[[1]]$space
selected_dim <- shapsepace_passeriformes_suborder_family[[1]]$dimensions
consensus_tree <- shapsepace_passeriformes_suborder_family[[1]]$consensus_tree
trees_list <- shapsepace_passeriformes_suborder_family[[1]]$trees_list
```

```{r, parametrise_the_model, eval = FALSE}
## Set up the parametrising chains models
param_MCMCglmm <- make.mini.chains(data         = shapespace,
                                   dimensions   = selected_dim,
                                   tree         = consensus_tree,
                                   trait.family = "gaussian",
                                   randoms      = c("global", "level1", "level2"),
                                   residuals    = "global",
                                   priors       = 0.02,
                                   verbose      = TRUE,
                                   parameters   = list(
                                       nitt   = 100000,
                                       thin   = 500,
                                       burnin = 0))

## Running the three MCMCglmm models
save(param_chains, file = "../Data/Processed/MCMCglmm/params_shapespace_8D_29levels_5k_chain1.rda")
```

```{r, get_model_parameters, eval = FALSE}
## Load the computed models
param_chains <- list()
for(i in 1:3) {
    load(paste0("../Data/Cluster/shapespace_passeriformes/param_chains/params_shapespace_passeriformes_chain", i, ".rda"))
    param_chains[[i]] <- params_shapespace_passeriformes[[1]]
}
## Extract the parameters from the parameter chains
est_params <- extract.parameters(param_chains)
```

## Set up the mini-chains models
shapespace_passeriformes <- make.mini.chains(
                                data         = shapespace,
                                dimensions   = selected_dim,
                                tree         = trees_list[sample(1:1000, 1000)],
                                trait.family = "gaussian",
                                randoms      = c("global", "level1", "level2"),
                                residuals    = "global",
                                priors       = est_params$priors,
                                verbose      = TRUE,
                                parameters   = list(
                                    nitt   = est_params$burnin + thin * samples,
                                    thin   = thin,
                                    burnin = est_params$burnin))
## Save the mini.chains
save(shapespace_passeriformes, file = "../Data/Cluster/shapespace_passeriformes/shapespace_passeriformes.mini.chains")
```
